---
title       : Making interactive presentations with RMarkdown
subtitle    : via Slidify
author      : Emily Dolson
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
widgets     : [bootstrap, quiz] # {mathjax, quiz, bootstrap}
ext_widgets : {rCharts: [libraries/nvd3]}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---
## RMarkdown allows you to make reproducible analyses

- Include 
  - Text 
  - Code
  - Code output

---
## Slidify lets you make slides in RMarkdown

- Slides will work the same across all operating systems and on the web
- If your data changes, just rebuild the presentation and your done!
- You can do really cool interactive plots and things 

---
## Easily include code
```{r}
library(ggplot2)
ggplot(data=Orange) + geom_line(aes(x=age, y=circumference, color=Tree))
```

---
## It's not just for R

```{r, engine='python'}
import numpy as np
print "Hello python"
```

--- &radio
## Interactive quiz widget
If `pwd` displays `/Users/backup`, and `-r` tells `ls` to display things in reverse order, what command will display:
```
pnas-sub/ pnas-final/ original/
```
1. ls pwd
2. ls -r -F
3. ls -r -F /Users/backup
4. _Either #2 or #3 above, but not #1_

*** .hint
This is a hint

*** .explanation
Since `/Users/backup` is an absolute path, it's okay to pass it to ls despite the fact that we're already there. It's unecessary, though.

--- 
## Interactive Chart

```{r, echo = F, results = 'asis'}
library(rCharts)
haireye = as.data.frame(HairEyeColor)
n1 <- nPlot(Freq ~ Hair, group = 'Eye', type = 'multiBarChart',
  data = subset(haireye, Sex == 'Male')
)
n1$print('chart1')
```
---
--- 
## How can you do this?

First, install slidify

```
require(devtools)
install_github("ramnathv/slidify", "dev") #Slidify isn't on CRAN, the normal R package manager, so we have to get it directly from Github. Sometimes this doesn't go as smoothly on Windows, but don't worry, the internet can help!
install_github("ramnathv/slidifyLibraries", "dev")
library(slidify)
```
